---
title: "Quality comparison of customer reviews of different smartphones on online marketplaces"
author: "Nadine Obeid, Clarence Koehle, Lucas Vogt and Arturo García Luna Beltrán"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme:
      bootswatch: united
---
```{r, include=FALSE}
source(here::here("script/unsupervised_learning/embedding/word_and_document_embedding.R"))
```
# Word embedding
The word embedding has been applied on our three reviews datasets: smartphone_reviews_final.csv, Apple_final.csv, and Samsung_final.csv. To embed words, we have decided to apply the `word2vec::word2vec` function using the `cbow` method. To visualize the results, we used the `uwot::umap` and the package `plot_ly`. In the following 2D and 3D graphs, only a subset of the words have been plotted in order to facilitate the visualization.

TODO **DISPLAY head of DF resulting from word embedding**

```{r}
graph_2d
graph_3d
```

Reading in word embedding models from three binary files: all_model.bin, apple_model.bin, and samsung_model.bin
Creating a 3D visualization of the word embeddings using the umap function from the uwot package and the plotly package
Preprocessing text data by removing punctuation, lowercasing and splitting the reviews into individual words, and embedding the documents using the document_embedding function and the embedded words matrix
Transforming the list of embedded documents into a matrix and removing attributes
Saving the embedded words and documents to two CSV files: embedded_words.csv and embedded_documents.csv
