---
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r, include=FALSE}
source(here::here("script/unsupervised_learning/embedding/document_embedding.R"))
```

## **Word Embedding**

The word embedding has been applied on our three reviews datasets: smartphone_reviews_final.csv, Apple_final.csv, and Samsung_final.csv. To embed words into 50-dimension vectors, we have decided to apply the `word2vec::word2vec` function using the `cbow` method with 30 iterations.

```{r, eval=FALSE, echo=TRUE}
# # Read data
all_reviews <- read.csv(here::here("data/smartphone_reviews_final.csv"))

# # Train word2vec model
# Embed each word into a 50-dimension vector
all_model <- word2vec(tolower(all_reviews$Reviews), type = "cbow", dim = 50, iter = 30)

# Transform the result into a matrix
embedded_words <- as.matrix(all_model)
```

Here is an overview of the resulting matrix:

```{r, echo=FALSE}
# # Matrix of embedded words
str(embedded_words)
```

To visualize the results in an interactive fashion, we used the `uwot::umap` and the package `plot_ly`. In the following 2D and 3D graphs, only a subset of the words have been plotted in order to facilitate the visualization.

```{r, eval=FALSE, echo=TRUE}
# # Read models
all_model <- read.word2vec(here::here("script/models/word2vec/all_model.bin"))

# # Create interactive plot of words
# source: https://cran.r-project.org/web/packages/word2vec/readme/README.html
embedded_words <- as.matrix(all_model)
viz <- umap(embedded_words, n_neighbors = 25, n_threads = 5, n_components = 3)

# Create the dataframe used for the plot
df  <- data.frame(word = gsub("//.+", "", rownames(embedded_words)), 
                  xpos = gsub(".+//", "", rownames(embedded_words)), 
                  x = viz[, 1], y = viz[, 2], z = viz[, 3],
                  stringsAsFactors = FALSE)

# Subset the dataframe
set.seed(456)
nb_words_to_display <- 1500
df  <- df[sample(1:nrow(df), nb_words_to_display),]

# Interactive 2D plot
graph_2d <- plot_ly(df, x = ~x, y = ~y, type = "scatter", mode = "text", text = ~word) %>% 
  layout(title = "2-Dimension word embedding (interactive graph)")

# Interactive 3D plot
graph_3d <- plot_ly(df, x = ~x, y = ~y, z = ~z, type = "scatter3d", mode = 'text', text = ~word) %>% 
  layout(title = "3-Dimension word embedding (interactive graph)")
```
```{r, fig.align='center', out.width='100%'}
graph_2d
graph_3d
```

## **Document Embedding**

We pre-processed the documents (reviews) by removing punctuation, lowercasing and splitting them into individual words. We then used the results from the word embedding to embed each review using the following function:

```{r, eval=FALSE, echo=TRUE}
# This function takes 2 arguments: A word vector (= sentence/document) and a matrix of embedded words
# It uses each embedded word values to return the value of the word vector
# Here the input word vector should be the words in a given document
# It assumes that by averaging the vector values of the words found in the
# document it's possible to summarize the information contained in a document
# as a vector 

document_embedding <- function(words, embedded_words_matrix){
  # Keep words present in the embedded_words_matrix
  look_up_words <- words[words %in% rownames(embedded_words_matrix)]
  
  # Document embedding
  # If there is more than one word in the document, do colSums
  if (length(look_up_words) > 1){
    document_embedding <- colMeans(embedded_words_matrix[look_up_words,])
    # If length = 1, don't run colSums as it will throw an error
  } else if (length(look_up_words == 1)){
    document_embedding <- embedded_words_matrix[look_up_words,]
    # If look_up_words is empty return a vector of zeros
  } else {
    document_embedding <- rep(0, ncol(embedded_words_matrix))
  }
  
  # Return embedded document
  return(document_embedding)
}

# # Embed documents (reviews) using document_embedding function
# Remove punctuation
all_reviews_sentences <- gsub('[[:punct:] ]+',' ', all_reviews$Reviews)

# Split sentences into words (to lower and trimmed) - Resulting in a list
document_words <- lapply(strsplit(tolower(all_reviews_sentences), " "), trimws)

# Document embedding using own document_embedding function
embedded_documents <- lapply(X = document_words, FUN = document_embedding, embedded_words_matrix = embedded_words)
```

Here is an overview of the resulting matrix:

```{r, echo=FALSE}
# # Matrix of embedded words
str(embedded_documents)
```
